Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-11 Grassmannian_cells.tex
Some polishing up through section 4.3

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
\begin{theorem}
  \label{thm:bb}
  \cite[Section 4]{bb}
  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is a vector bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
Indeed, we can trivialize each vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.

@@

Assume that $X=\bigoplus_{l=1}^m X_l$ is a direct sum decomposition of $X$ and fix a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $0=r_0<r_1<r_2<\cdots<r_{m-1}<r_m=n$ such that
\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
\begin{lemma}
  \label{le:usualGrass}
  Consider a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(r)=d(r')$ if $v_r,v_{r'}\in X_l$ for some $l$ and $d(r)\neq d(r')$ if $v_r\in X_l$ and $v_{r'}\in X_{l'}$ with $l\neq l'$.
  Then under the $\CC^*$-action determined by $d$, we have $U\in\Gr_k(X)^{\C^\ast}$ if and only if $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{lemma}
\begin{proof}
  Assume $U=\bigoplus_{l=1}^m U\cap X_l$.
  Then any $u\in U$ can be written uniquely as $u=\sum_{l=1}^m u_l$ for some $u_l\in U\cap X_l$.
  It follows that $t.u=\sum_{l=1}^m t.u_l=\sum_{l=1}^m t^{d(r_l)}u_l\in\bigoplus_{l=1}^m U\cap X_l=U$ and thus $t.U=U$.

  For the reverse direction, assume $U\in X_{\bfi}$ is a torus fixed point represented by the matrix $M(U)$.
  Then, if~$v_{i_q}\in X_l$, the assumptions on $d$ imply $M(U)_{qr}=0$ unless $r_{l-1}+1\le r\le r_l$.
  That is, $M(U)$ has the shape of a block matrix representing the decomposition $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{proof}
The next step is to generalize this to quiver Grassmannians.
Let $Q$ be an acyclic quiver.
We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
We can consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which can be extended linearly to each $X_i$.
Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
In general, this does not induce a torus action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
\begin{lemma}
  Let $X$ be a representation of $Q$ which can be lifted to $\hat Q$.
  Fix an integer $c_\alpha\in\ZZ$ for each~$\alpha\in Q_1$.
  Suppose $d:\hat Q_0\to\ZZ$ satisfies $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for each arrow $\alpha:i\to j$ of $Q$ and each $\chi\in A_Q$.
  Then the torus action on $X$ determined by $d$ induces a torus action on $\Gr_\bfe(X)$.
\end{lemma}
\begin{proof} 
  Fix $U\in\Gr_\bfe(X)$ and consider $u_i\in U_i$.
  Since $U$ is a subrepresentation, for an arrow $\alpha:i\to j$ of $Q$ we may write $X_\alpha(u_i)=u_j$ for some $u_j\in U_j$.

@@

The next result provides conditions required of the map $d:\hat Q_0\to\ZZ$ needed to get an analogue of Lemma~\ref{le:usualGrass}
\begin{lemma}
  \label{le:degree condition} 
  Let $\hat X$ be an indecomposable representation of $\hat Q$.
  There exists $d:\supp(\hat X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
  \begin{enumerate}
    \item for $(i,\chi),\,(i,\chi')\in\supp(X)$ with $\chi\neq\chi'$, we have $d(i,\chi)\ne d(i,\chi')$;
    \item for $(i,\chi),\,(j,\chi')\in\supp(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  For convenience we introduce the notation $Q_1=\{\alpha_1,\ldots,\alpha_n\}$.
  Since $X$ is finite-dimensional and indecomposable, the support quiver $\supp(X)$ is a connected and finite subquiver of $\hat Q$.
  In order to prove the statement, we may assume that $(i',0)\in\supp(X)$ for some $i'\in Q_0$.
  Let $K$ be the maximal length of a path in $\supp(X)$ starting or ending in $(i',0)$ such that the underlying graph of the path has no cycles.
  This implies that, for $(i,\chi)\in\supp(X)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have $|\kappa_l|\leq K$.

  Set $c_{\alpha_1}=1$ and choose $c_{\alpha_l}$ recursively in such way that 
  \[c_{\alpha_l}\geq 2(K+1)\sum_{k=1}^{l-1} c_{\alpha_k}\]
  for $l=2,\ldots,n$.  
  Then let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i,\chi):=f(\chi)$ for $(i,\chi)\in\supp(X)$.
  %In particular, for $(i',\chi)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have
  %\[d(i',\chi)=\sum_{l=1}^n \kappa_l c_{\alpha_l}.\]

@@

  By definition, we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ when $(j,\chi+e_\alpha)\in\supp(X)$.
  Now assuming $d(j,\chi')-d(i,\chi)=c_\alpha$, an analogous argument to the one above shows that $\chi'=\chi+e_\alpha$.
\end{proof}

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}\label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $X$.
  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering.
\end{proof}
The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k)}_0$ is a tree.
Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_i$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$, we obtain the following result.
\begin{corollary}
Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q^{(k)}}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$

\begin{corollary}\label{fpoly}
Let $X$ be a representation which can be lifted to the universal covering quiver.
\begin{enumerate}
\item 
If  $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_{ \tbfe}(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
\item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[x_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[x_i\mid i\in Q_0]$ given by $S(x_{(i,w)})=x_i$ for all $i\in Q_0$ and $w\in W_Q$.
\end{enumerate} 
\end{corollary}
An important special case for this is the case of exceptional representations. In this case the quiver Grassmannians $\Gr_\tbfe(X)$ are smooth by \cite[Corollary 4]{cr}. Moreover, every exceptional representation is a tree module by \cite{rin1} which means that it can be lifted to the universal covering.

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
Write $\Ind(K(n),d)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$. As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind(K(n),d)$.
\begin{proposition} \label{indecomposables}
  Let $m\geq 1$ and $d(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. The action of $\GL_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),d(m,r))$.
\end{proposition}
\begin{proof}
  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_{d(1,r)}(K(n))$.
  As the reflection functors preserve indecomposability and isomorphism classes, by Lemma~\ref{compatibleGSigma}, for every $g\in\GL_n(\CC)$, we obtain a commutative diagram
  \[\xymatrix{\Ind(K(n),d(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),d(m+1,r))\ar[d]^g\\
    \Ind(K(n),d(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),d(m+1,r))}.\]
  As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}

@@

  Proposition~\ref{pro:indecomposables} and~\ref{indecomposables} imply that all quiver Grassmannians $\Gr_\bfe(M)$ for a fixed $\bfe\in\NN^{Q_0}$ where $M\in\Ind(K(n),\udim P_{m+1}^V)$ are isomorphic.
  With other words we use that all indecomposables are truncated preprojectives.

>>>>

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
\begin{theorem}
  \label{thm:bb}
  \cite[Section 4]{bb}
  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine vector bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
Indeed, we can trivialize each affine vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.

@@

Assume that $X=\bigoplus_{l=1}^m X_l$ is a direct sum decomposition of $X$ and fix a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist indices $0=r_0<r_1<r_2<\cdots<r_{m-1}<r_m=n$ such that
\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
\begin{lemma}
  \label{le:usualGrass}
  Consider a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(r)=d(r')$ if $v_r,v_{r'}\in X_l$ for some $l$ and $d(r)\neq d(r')$ if $v_r\in X_l$ and $v_{r'}\in X_{l'}$ with $l\neq l'$.
  Then under the $\CC^*$-action determined by $d$, we have $U\in\Gr_k(X)^{\C^\ast}$ if and only if $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{lemma}
\begin{proof}
  Assume $U=\bigoplus_{l=1}^m U\cap X_l$.
  Then any $u\in U$ can be written uniquely as $u=\sum_{l=1}^m u_l$ for some $u_l\in U\cap X_l$.
  It follows that $t.u=\sum_{l=1}^m t.u_l=\sum_{l=1}^m t^{d(r_l)}u_l\in\bigoplus_{l=1}^m U\cap X_l=U$ and thus $t.U=U$.

  For the reverse direction, assume $U\in X_{\bfi}$ is a torus fixed point represented by the matrix $M(U)$.
  Then, if~$v_{i_q}\in X_l$, the assumptions on $d$ imply $M(U)_{qr}=0$ unless $r_{l-1}+1\le r\le r_l$.
  That is, $M(U)$ has the shape of a block matrix representing the decomposition $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{proof}
The next step is to generalize this to quiver Grassmannians.
Let $Q$ be an acyclic quiver.
Choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
We consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which is then extended linearly to each $X_i$.
Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
In general, this does not induce a torus action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
\begin{lemma}
  Let $X$ be a representation of $Q$ which can be lifted to $\hat Q$.
  Fix an integer $c_\alpha\in\ZZ$ for each~$\alpha\in Q_1$.
  Suppose $d:\hat Q_0\to\ZZ$ satisfies $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for each arrow $\alpha:i\to j$ of $Q$ and each $\chi\in A_Q$.
  Then the torus action on $X$ determined by $d$ induces a torus action on $\Gr_\bfe(X)$.
\end{lemma}
\begin{proof} 
  Fix $U\in\Gr_\bfe(X)$ and consider $u_i\in U_i$.
  Since $U$ is a subrepresentation, for an arrow $\alpha:i\to j$ of $Q$ we may write $X_\alpha(u_i)=u_j$ for some $u_j\in U_j$.

@@

The next result provides the conditions on the map $d:\hat Q_0\to\ZZ$ needed to get an analogue of Lemma~\ref{le:usualGrass}
\begin{lemma}
  \label{le:degree condition} 
  Let $\hat X\in\rep\hat Q$ be an indecomposable representation of $\hat Q$.
  There exists $d:\supp(\hat X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
  \begin{enumerate}
    \item for $(i,\chi),\,(i,\chi')\in\supp(\hat X)$ with $\chi\neq\chi'$, we have $d(i,\chi)\ne d(i,\chi')$;
    \item for $(i,\chi),\,(j,\chi')\in\supp(\hat X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  For convenience we introduce the notation $Q_1=\{\alpha_1,\ldots,\alpha_n\}$.
  Since $\hat X$ is finite-dimensional and indecomposable, the support quiver $\supp(\hat X)$ is a connected and finite subquiver of $\hat Q$.
  In order to prove the statement, we may assume that $(i',0)\in\supp(\hat X)$ for some $i'\in Q_0$.
  Let $K$ be the maximal length of a path in $\supp(\hat X)$ starting or ending in $(i',0)$ such that the underlying graph of the path has no cycles.
  This implies that, for $(i,\chi)\in\supp(\hat X)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have $|\kappa_l|\leq K$.

  Set $c_{\alpha_1}=1$ and choose $c_{\alpha_l}$ recursively in such way that 
  \[c_{\alpha_l}\geq 2(K+1)\sum_{k=1}^{l-1} c_{\alpha_k}\]
  for $l=2,\ldots,n$.  
  Then let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(e_\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i,\chi):=f(\chi)$ for $(i,\chi)\in\supp(\hat X)$.
  %In particular, for $(i',\chi)$ with $\chi=\sum_{l=1}^n \kappa_l e_{\alpha_l}$, we have
  %\[d(i',\chi)=\sum_{l=1}^n \kappa_l c_{\alpha_l}.\]

@@

  By definition, we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ when $(j,\chi+e_\alpha)\in\supp(\hat X)$.
  Now assuming $d(j,\chi')-d(i,\chi)=c_\alpha$, an analogous argument to the one above shows that $\chi'=\chi+e_\alpha$.
\end{proof}

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}\label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
  Then the torus action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced torus actions on the usual Grassmannian $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
\end{proof}
The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k)}_0$ is a tree.
Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_i$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$.
If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$, we obtain the following result.
\begin{corollary}
Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q^{(k)}}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].$$

\begin{corollary}
  \label{fpoly}
  Let $X$ be a representation which can be lifted to the universal covering quiver.
  \begin{enumerate}
    \item If $\Gr_\bfe(X)$ is smooth and $\Gr^{\tilde Q}_\tbfe(\tilde X)$ has a cell decomposition into affine spaces, then $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
    \item We have $F_X=SF_{\tilde X}$ where $SF_{\tilde X}$ is obtained from $F_{\tilde X}$ by applying $S:\ZZ[y_{(i,w)}\mid i\in Q_0,w\in W_Q]\to\ZZ[y_i\mid i\in Q_0]$ given by $S(y_{(i,w)})=y_i$ for all $i\in Q_0$ and $w\in W_Q$.
  \end{enumerate} 
\end{corollary}
An important special case for this is the case of exceptional representations.
In this case the quiver Grassmannians $\Gr_\bfe(X)$ are smooth by \cite[Corollary 4]{cr}.
Moreover, every exceptional representation is a tree module by \cite{rin1} which means that it can be lifted to the universal covering.

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$. As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
\begin{proposition} 
  \label{indecomposables}
  Let $m\geq 1$ and $d(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
  The action of $\GL_n(\CC)$ is transitive on $\Ind\big(K(n),d(m,r)\big)$.
\end{proposition}
\begin{proof}
  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
  As the reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
  \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
    \Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}&\Ind\big(K(n),d(m+1,r)\big)}.\]
  As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}

@@

  Propositions~\ref{pro:indecomposables} and~\ref{indecomposables} imply that the quiver Grassmannians $\Gr_\bfe(M)$ for $M\in\Ind\big(K(n),\udim P_{m+1}^V\big)$ are all isomorphic for a fixed $\bfe\in\NN^{Q_0}$.
  In other words, we use that all indecomposables with this dimension vector are truncated preprojectives.
